\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-10 appendix-1.Rmd
Decluttred appendix All external string based tables are converted into csv

```{r factormp, warning=F}
map <- readr::read_csv("Table_raw/map_stat")
map1 <- (map$`MAP Statistic`)

map1 <- MOTE::apa(map1,5,F)
map1 <- as.character(map1)
map1 <- as.data.frame(map1)
colnames(map1) <- "MAP Statistics"
map2 <- map[,-c(1,2)]
map3 <- cbind(map1, map2)

papaja::apa_table(map3, caption = "Map Statistics")
```

```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
knitr::include_graphics('Manuscript.figures/EFAResidual.png')

@@

@@

```{r midesp, warning=F, message=F}
mides_kable %>% 
  kable_styling(latex_options = c("scale_down")) 
```

```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F1testinfo.png')
```

```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F2testinfo.png')
```

```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F3testinfo.png')
```

```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F4testinfo.png')
```

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5testinfo.png')
```

```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
knitr::include_graphics("Manuscript.figures/personfit.png")
```

>>>>

**Disclaimer**: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!

LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.

**Instruction:**

"Please indicate how often you performed the following behaviours in the **past 4 weeks.**"

```{r longdata, include =F}
long <- readxl::read_excel("Table_raw/LEBA Long.xlsx")
long <- long %>% mutate_all(~ replace_na(.x, " "))
```

```{r LEBAlong, warning =F}
long %>% 
apa_table(landscape =T,caption ="LEBA Long Form (23 Items) ",  font_size = "footnotesize", align = c("p{15cm}", rep("p{1cm}", ncol(long)))) 
```

```{r longreldata, include =F}
long.rel <- readxl::read_excel("Table_raw/LEBA_longs_structure.xlsx")
long.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
```

```{r longrel, warning =F}
long.rel %>% 
apa_table(landscape =F,caption ="LEBA Long Form (23 Items):Latent Structure and Reliability ",  font_size = "footnotesize")
```

```{r shortdata, include =F}
short <- readxl::read_excel("Table_raw/LEBA_Short.xlsx")
short <-short%>% mutate_all(~ replace_na(.x, " "))
```

```{r LEBAshort, warning =F}
short %>% 
apa_table(landscape =T,caption ="LEBA Short Form (18 Items) ",  font_size = "footnotesize", align = c("p{15cm}", rep("p{1cm}", ncol(short)))) 
```

```{r shortreldata, include =F}
short.rel <- readxl::read_excel("Table_raw/LEBA_short_structure.xlsx")
short.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
```

```{r lshortrel, warning =F}
short.rel %>% 
apa_table(landscape =F,caption ="LEBA Short Form (18 Items):Latent Structure ",  font_size = "footnotesize")
```

```{r factormp, warning=F}
map <- readr::read_csv("Table_raw/map_stat.csv")
map1 <- (map$`MAP Statistic`)
map1 <- MOTE::apa(map1,5,F)
map1 <- as.character(map1)
map1 <- as.data.frame(map1)
colnames(map1) <- "MAP Statistics"
map2 <- map[,-c(1,2)]
map3 <- cbind(map1, map2)

@@

```{r map}
papaja::apa_table(map3, caption = "Minimum Average Partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
```

@@

```{r midesp, warning=F, message=F, results='asis'}
mides_kable %>% 
  kable_styling(latex_options = c("scale_down")) 
```

```{r MinRes, include=F}
library(psych)
library(tabledown)
library(kableExtra)#without this pdf rendering will not happen

data <- readRDS("leba_2021-09-08.rds")

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

names(sem.data)[names(sem.data) == "item1"] <- "item01"
names(sem.data)[names(sem.data) == "item2"] <- "item02"
names(sem.data)[names(sem.data) == "item3"] <- "item03"
names(sem.data)[names(sem.data) == "item4"] <- "item04"
names(sem.data)[names(sem.data) == "item5"] <- "item05"
names(sem.data)[names(sem.data) == "item6"] <- "item06"
names(sem.data)[names(sem.data) == "item7"] <- "item07"
names(sem.data)[names(sem.data) == "item8"] <- "item08"
names(sem.data)[names(sem.data) == "item9"] <- "item09"

### EFA data
EFA.data <- sem.data[1:428, ]
#Polychoric Correlation matrix

correlations <- psych::polychoric(EFA.data, correct = 0)

#Supplementary EFA with Minres Extraction

fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
                residuals = TRUE, SMC = TRUE, n.obs =428)
EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14))

correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)

fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14, item34, item47, item21, item13))

correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)

fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)

minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
```

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
```

```{r sixFac, include=F}
# EFA with 6 factor (rejected)

#correlations <- polychoric(EFA.factor, correct = 0)

fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23))

correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41))

correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)

fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29))

correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)

fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29, item19))

correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)

fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)

# Residuals
residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRRR= sum(residual.6F>abs(.05), na.rm =T)
print(BigRRR)

#Total number of off diagonal elements in the data matrix
totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2

# Proportion of off-diagonal elements >.10
sumRRR <- sum(BigRRR/totRRR*100)

#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
#abline(h =65, lwd = 2, lty = 2)
#abline(v =.05,lwd = 2, lty = 2)
sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
```

```{r sixFacTab}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
```

```{r DataAppB, include=FALSE}
data <- readRDS("leba_2021-09-08.rds")

#Separating the EFA and CFA(only items)
sem.data <- data[, 9:56] #EFA & CFA data
## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
names(sem.data)[names(sem.data) == "item1"] <- "item01"
names(sem.data)[names(sem.data) == "item2"] <- "item02"
names(sem.data)[names(sem.data) == "item3"] <- "item03"
names(sem.data)[names(sem.data) == "item4"] <- "item04"
names(sem.data)[names(sem.data) == "item5"] <- "item05"
names(sem.data)[names(sem.data) == "item6"] <- "item06"
names(sem.data)[names(sem.data) == "item7"] <- "item07"
names(sem.data)[names(sem.data) == "item8"] <- "item08"
names(sem.data)[names(sem.data) == "item9"] <- "item09"
EFA.data <- sem.data[1:428, ]

correlations <- psych::polychoric(EFA.data, correct = 0)

```{r ggplot2AppB, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        plot.title = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

```{r EFAAppB, include=FALSE}
fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item24, item37, item22, item05,
                                        item28, item30, item39,item23, item45, item06, item29, item02, item41))

correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14))

correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14, item43, item42))

correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)

fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
```

```{r factordetailsAppB, include=FALSE}
#Preparing the EFA table
efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
```

```{r efaunmerged}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
```

```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}

library(Hmisc)
fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item05,
                                        item28,item39,item23, item45, item06, item29, item02, item41, item30))

correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)

fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
reduced.model.6F.2 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item05,
                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25))
correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.3 <- dplyr::select(EFA.data ,
                                    -c(item32, item34, item44,item24, item37, item22, item05,
                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25, item18))
correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
```

```{r EFAsix}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
```

```{r tzdata, include=F}
tz <- read_csv("Table_raw/timezone.csv")
tz <- tz[,-1]
colnames(tz) <- c("Timezone", "Number of Participants")
participants <- sum(tz[, 'Number of Participants'])
```

```{r tztable}
apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical Location of the participants (n =690)")
```

```{r unmerged-data, include =F}
unmerged <- read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
```

```{r unmertab}
apa_table(unmerged , longtable =T, font_size = "footnotesize")
```

```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
```

```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2. All items cariied information across the latent trait continuum. Item 09 carried the lowest information however its information peak was highr than .20.', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
```

```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3. Item 30 and 41 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
```

```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
```

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5. Three items: 25, 04, 01 carriedlow information. However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.  Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 600)
```

```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 600)
```
